---
title: "upload_help"
author: "David Barkemeyer"
date: "21 4 2021"
output: md_document
---

### Overview

You may upload your own set of distributions by following these steps:

* Install the [{distributional}](https://github.com/mitchelloharawild/distributional) package
* Create a data structure of distributions (see below) in your R session
* Store this data structure in the `.rds` file format
* Upload the `.rds` file inside this application

### Data Structures

```{r, eval=FALSE}
library(distributional)
library(readr)
```

#### Vector of distributions

```{r, eval=FALSE}
x <- dist_normal(mu = 0, sigma = 1:5)
write_rds(x, "dist_vector.rds")
```

#### List of distributions

If you need the flexibilty to differentiate between active and inactive distributions, you may store a list of distributions.

```{r, eval=FALSE}
x <- list(
  active = dist_normal(mu = 0, sigma = 1:5),
  inactive = dist_normal(mu = -2:2, sigma = 1)
)
write_rds(x, "dist_list.rds")
```

##### Options

Further options can be set as fields on the top level (same level as `active` and `inactive`):

* `min`: Initial x axis left limit
* `max`: Initial x axis right limit

#### Colors

If you want to control the initial color of a distribution, you can add a color field to a distribution on the same level as the distribution parameters.

```{r, eval=FALSE}
x <- dist_normal(mu = 0, sigma = 1:5)

# Second distribution shall be red
x[[2]]$color <- "#ff0000"

# Apply color scale
library(scales)
color_scale <- col_numeric(palette(), 1:5)
for (i in 1:5) x[[i]]$color <- color_scale(i)
```
